Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-17 WSSSPE1_report/WSSSPE1_summary_report.tex
some more text to section 9

\subsection{Utility Software}
The General Purpose Software applicable to a generic task and/or enabling other
software to run by providing suitable environment. For example, collaborative
development, Workflow and scripting frameworks, visualization frameworks.
\subsection{Scientific Software}
Special Purpose Software that was developed specifically for a target use-case
scenario or keeping some fixed/frozen requirements in mind.  
Domain science
oriented software developed to solve domain science problems, eg MINRES-QLP.
\subsection{Infrastructure Software}
Infrastructure oriented software developed to better utilize new
infrastructure, eg. MVAPICH.
%
%\begin{itemize}
%  \item mvapich, Cactus, DUNE
%  \item gateways, github, VisIT, visTrails, PAAS
%  \item SimGrid, Swift, Galaxy
%  \item FastMath, R/qtl, MINRES-QLP
%  \item OWL/RDF, AMR/multiphysics, Globus-Genomics
%\end{itemize}
%

>>>>

\subsection{Utility Software}
Utility software has a potential of broadest community impact. This is
especially relavent in the modern era of social computing. In the context of
this paper, a utility software could be defined as a general purpose software
applicable to one or many generic tasks and/or enabling other software to run
by providing suitable environment. For example, collaborative development
framework such as \emph{github} and \emph{bitbucket}, Workflow and scripting
frameworks such as \emph{Galaxy}, \emph{Swift} and \emph{VisTrails},
visualization frameworks such as \emph{visIT}. Often projects start with
specific, small set of requirements and users in mind but expand to provide
generic functionalities and appeal to a wider user community.

\subsection{Scientific Software}
Special Purpose Software that was developed specifically for a target use-case
scenario or keeping some fixed/frozen requirements in mind.  Domain science
oriented software developed to solve domain science problems, eg MINRES-QLP.

\subsection{Infrastructure Software}
Infrastructure oriented software developed to better utilize new
infrastructure, eg. MVAPICH.
%
%\begin{itemize}
%  \item mvapich, Cactus, DUNE
%  \item gateways, github, VisIT, visTrails, PAAS
%  \item SimGrid, Swift, Galaxy
%  \item FastMath, R/qtl, MINRES-QLP
%  \item OWL/RDF, AMR/multiphysics, Globus-Genomics
%\end{itemize}
%
